BurgerTown Presents: Open Adcess

### 2017-05-19 future-work.tex
Update future-work.tex

\subsection{ACM Seizes Means of Production}
The ACM has successfully seized the means of production. While a soviet of 
technicians along the lines of what Veblen had proposed was discussed in these 
pages in the fine print of ads for a supersoda that only engineers in the 
``lifehacking" crowd could possibly have read, the revolution was not thanks
to the engineers---who, even when fully aware that the ``industrial dictatorship
of the captain of finance" was ``held on sufferance of the engineers" and ``liable
to at any time be discontinued at their discretion, as a matter of convenience" \cite{Veblen}, were
unable to commit to revolution.
Instead, the work of revolution was done through ``the long march through the institutions,"
as Rudi Dutschke put it. THat is, we had the baristas do it. They ``get" solidarity.

The mills that are now used to power our servers were previously used to grind
healing crystals into a fine powder at night, when Medicaid recipients had gone home
for the evening after powering the ``digital doctor" they'd been allowed to consult by day
and the keggers of the politicians who had successfully block-granted Medicaid.
This powder was slipped into the coffee of unsuspecting CEOs, where it worked to
slowly make them more susceptible to the messages of the ACM---to, as Veblen put it,
``understand that the whole fabric of credit and corporation finance is a tissue of make-believe"
and that, after the revolution, the same technicians and engineers could manage the same
industrial production processes, though organized around the common interest (full production,
equitable distribution) and not the interests of absentee owners of monopolistic firms \cite{Veblen}.
After years of crystal ingestion, the CEOs of the world's largest companies 
ceded control of their companies to the ACM. (Except the Virgos, who did not cede control until
the baristas sent rockets into space to forcibly alter the astrological conditions in the revolution's favor.)
We are happy to announce that there currently exist no companies other than the
ACM.

>>>>

\subsection{ACM Seizes Means of Production}
The ACM has successfully seized the means of production. While a soviet of 
technicians along the lines of what Veblen had proposed was discussed in these 
pages in the fine print of ads for a supersoda that only engineers in the 
``lifehacking" crowd could possibly have read, the revolution was not thanks
to the engineers---who, even when fully aware that the ``industrial dictatorship
of the captain of finance" was ``held on sufferance of the engineers" and ``liable
to at any time be discontinued at their discretion, as a matter of convenience" \cite{Veblen}, were
unable to commit to revolution.
Instead, the work of revolution was done through ``the long march through the institutions,"
as Rudi Dutschke put it. That is, we had the baristas do it. They ``get" solidarity.

The mills that are now used to power our servers were previously used to grind
healing crystals into a fine powder at night, when Medicaid recipients had gone home
for the evening after powering the ``digital doctor" they'd been allowed to consult by day
and the keggers of the politicians who had successfully block-granted Medicaid.
This powder was slipped into the coffee of unsuspecting CEOs, where it worked to
slowly make them more susceptible to the messages of the ACM---to, as Veblen put it,
``understand that the whole fabric of credit and corporation finance is a tissue of make-believe"
and that, after the revolution, the same technicians and engineers could manage the same
industrial production processes, though organized around the common interest (full production,
equitable distribution) and not the interests of absentee owners of monopolistic firms \cite{Veblen}.
After years of crystal ingestion, the CEOs of the world's largest companies 
ceded control of their companies to the ACM. (Except the Virgos, who did not cede control until
the baristas, after consulting their ``Sun, Love and Passion" Astrology Report, sent rockets into space to forcibly alter the astrological conditions in the revolution's favor.)
We are happy to announce that there currently exist no companies other than the
ACM.
